---
title: "Video Games Sales with Ratings"
subtitle: "Math 4322 Final Project, Group 24"
author: "Jay Nguyen, Alonso Munoz, Andrew-Son Le"
date: "30 April 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,message=FALSE,warning=FALSE,results='hide'}
library(randomForest) # testing stuff
load("~/Desktop/paper.RData")
```
```{r}
varImpPlot(rf_full)
summary(lm_full)
```

## Introduction
fasdfas  

Just temporary

A multiple regression model follows $Y = \beta_0 + \beta_1*X_1 + \beta_2*X_2 + ... + \beta_p*X_p + \varepsilon$ where $X_p$ represents our predictors and $\beta_p$ represents the coefficients related to the predictors in the linear model. The goal of the multiple linear regression model is to estimate each $\beta_p$ coefficient.

m ~$\sqrt{p}$

Global_Sales = $\beta_0$ + Platform * $\beta_1$ + Year_of_Release * $\beta_2$ + Genre * $\beta_3$ + Critic_Score * $\beta4$ + User_Score * $\beta_5$ + Rating * $\beta_6$ + $\varepsilon$. 

## Linear Model
asdfasd  

## Random Forest Model
asdfasd  

## Conclusion
asdfasdf  
